---
toc: true
toc_float: true
---

# FAIR data entity test

## Purpose of this document

This document tests if you can read data and see a row from that data on your machine.

## Open the data from your local machine

> Make sure the data is copied into local-data/ there is a listing in the .gitignore that ensures anything in this folder ignored when pushing to the github. 

This folder does not push your development data to the internet, and ensures privacy. 

## Install readxl to read excel file into R

```{r}
# Install the readxl package if not already installed
if (!requireNamespace("readxl", quietly = TRUE)) {
  install.packages("readxl")
}


# Load the readxl library
library(readxl)
library(tidyverse)

```

# Read and display a row of data

```{r}
# Read the .xlsx file
SDGPref_Arunachal_raw <- read_excel("local-data/SDGPreferences_Arunachal.xlsx")

# Dimensions of data
dim(SDGPref_Arunachal_raw)

# Display the first rows of the data
head(SDGPref_Arunachal_raw, 1)
```

# Test an assumption about the data

> Nerds, I'm going to write a function that finds the set of minimal unique combination of columns that define a row in a table in R unless we find a tool that does that for me. 

We assume the rows of `SDGPref_Arunachal_raw` are uniquely identified by `Respondents`.

```{r}
n_unique_key <- SDGPref_Arunachal_raw |>
  # here is where we set the assumption about the unique combination of columns
  select(Respondents) |>
  # this line removes duplicates (which shouldn't exist)
  distinct() |>
  # count how many 
  nrow()

# print result
n_unique_key

```

We compare with the number of rows in `SDGPref_Arunachal_raw`.

```{r}
n_unique_key == nrow(SDGPref_Arunachal_raw)

```

