# FAIR staging of source-specific data

```{r setup staging, include = FALSE}
knitr::opts_chunk$set(
	error = TRUE,
	message = FALSE
	)
```

## Input

Raw datasets provided.

## Output

Clean datasets representing one extraction of one entity of interest.

## Set up

```{r }
#| message: false

library(tidyverse)
library(readxl)
library(here)


```

### Clean column names helper

```{r}
cleanup_colnames <- function(df) {
  names(df) <- names(df) |>
    tolower() |>
    (\(x) gsub("[^a-z0-9]+", "_", x))() |>
    (\(x) gsub("^_|_$", "", x))() |>
    (\(x) ifelse(grepl("^[0-9]", x), paste0("x", x), x))()
  df
}

```


## get the data

### SDG labelling

```{r}
# Read file and clean names
staging_sdg <- read_csv(here("data-raw", "SDG.csv")) |> 
	cleanup_colnames() |>
	rename(sdg_id = sdg, sdg_label = name)

# Dimensions of data
dim(staging_sdg)

print(staging_sdg)

```


### SDGPref_Arunachal_raw 

Arunchal GDP preference responses, wide format. 

```{r}

# Read the provided .xlsx file
responses_arunachal <- read_excel(here("data-raw", "SDGPreferences_Arunachal.xlsx")) |>
	cleanup_colnames() |>
	mutate(
		respondent_id = str_c("respondent_", respondents, "_arunachal")
	) |>
	select(respondent_id, everything(), -respondents, -x9)

# Dimensions of data
dim(responses_arunachal)

staging_respondent_arunachal <- responses_arunachal |>
	select(c(respondent_id, age, gender)) |>
	mutate(region = "arunachal",
	 # this is so it's the same as the tehri gender
  # there is one prefer not to say in the tehri
  
  gender = case_when(
    gender == "Male" ~ "Man",
    gender == "Female" ~ "Woman",
    TRUE ~ gender))

staging_top_3_arunachal <- responses_arunachal [, 1:4] |>
	pivot_longer(cols = -respondent_id,
		names_to = "preference", 
		values_to = "sdg_id") |>
		mutate(response_id = str_c(respondent_id, '_', preference))

```


### Tehri

```{r}

# Read file and clean names
responses_tehri <- read_delim(
	here("data-raw", "Dam_and_You_-_all_versions_-_labels_-_2023-06-21-12-49-55.csv"),
	delim=";") |>
	cleanup_colnames() |>
	mutate(
		respondent_id = str_c("respondent_", 1:n(), "_tehri")
		) |>
	select(respondent_id, everything())

# Dimensions of data
dim(responses_tehri)

staging_respondent_tehri <- responses_tehri |>
  select(
		respondent_id, 
		displacement = please_select_which_group_the_respondent_belongs_to, 
		age = what_is_your_age, 
		gender = what_gender_do_you_identify_with) |>
  mutate(region = "tehri") 

staging_top_3_tehri <-  responses_tehri[, c(1, 69:71)] |>
  rename(
    x1st_preference = x1st_choice_68,
    x2nd_preference = x2nd_choice_69,
    x3rd_preference = x3rd_choice_70
	) |> 
	pivot_longer(cols = -respondent_id,
		names_to = "preference", 
		values_to = "sdg_label") |>
		mutate(response_id = str_c(respondent_id, "_", preference))

staging_top_3_tehri

```


## Check source-specifc semantic entity data

```{r}
#| message: true

source(here("R", "ge_unique_key.R"))

ge_unique_key(staging_respondent_arunachal, "respondent_id")
ge_unique_key(staging_respondent_tehri, "respondent_id")
ge_unique_key(staging_top_3_arunachal, "response_id")
ge_unique_key(staging_top_3_tehri, "response_id")
ge_unique_key(staging_sdg, "sdg_id")

```


## Write source-specific semantic entity data

```{r}
staging_path <- here("pipeline", "pipeline-data")

write_csv(staging_sdg, here(staging_path, "staging_sdg.csv"))
write_csv(staging_top_3_arunachal, here(staging_path, "staging_top_3_arunachal.csv"))
write_csv(staging_top_3_tehri, here(staging_path, "staging_top_3_tehri.csv"))
write_csv(staging_respondent_arunachal, here(staging_path, "staging_respondent_arunachal.csv"))
write_csv(staging_respondent_tehri, here(staging_path, "staging_respondent_tehri.csv"))


```


