# FAIR  of source-specific data

## Input

Raw datasets provided.

## Output

Clean datasets representing one extraction of one entity of interest.

## Set up

```{r }
#| message: false

library(tidyverse)
library(readxl)
library(here)


```

### Clean column names helper

```{r}
cleanup_colnames <- function(df) {
  names(df) <- names(df) |>
    tolower() |>
    (\(x) gsub("[^a-z0-9]+", "_", x))() |>
    (\(x) gsub("^_|_$", "", x))() |>
    (\(x) ifelse(grepl("^[0-9]", x), paste0("x", x), x))()
  df
}

```


## get the data



### SDGPref_Arunachal_raw 

Arunchal GDP preference rankings, wide format. 

```{r}

# Read the provided .xlsx file
responses_arunachal <- read_excel(here("data-raw", "SDGPreferences_Arunachal.xlsx")) |>
	cleanup_colnames() |>
	mutate(
		respondent_id = str_c("respondent_", respondents, "_arunachal")
	) |>
	select(respondent_id, everything(), -respondents, -x9)

# Dimensions of data
dim(responses_arunachal)

source_respondent_arunachal <- responses_arunachal |>
	select(c(respondent_id, age, gender)) |>
	mutate(region = "arunachal",
	 # this is so it's the same as the tehri gender
  # there is one prefer not to say in the tehri
  
  gender = case_when(
    gender == "Male" ~ "Man",
    gender == "Female" ~ "Woman",
    TRUE ~ gender))

source_top_3_arunachal <- responses_arunachal [, 1:4] |>
	pivot_longer(cols = -respondent_id,
		names_to = "preference", 
		values_to = "sdg_id") |>
		mutate(response_id = str_c(respondent_id, '_', preference))

```


### Tehri

```{r}

# Read file and clean names
responses_tehri <- read_delim(
	here("data-raw", "Dam_and_You_-_all_versions_-_labels_-_2023-06-21-12-49-55.csv"),
	delim=";") |>
	cleanup_colnames() |>
	mutate(
		respondent_id = str_c("respondent_", 1:n(), "_tehri")
		) |>
	select(respondent_id, everything())

# Dimensions of data
dim(responses_tehri)

source_respondent_tehri <- responses_tehri |>
  select(
		respondent_id, 
		displacement = please_select_which_group_the_respondent_belongs_to, 
		age = what_is_your_age, 
		gender = what_gender_do_you_identify_with) |>
  mutate(region = "tehri") 

source_top_3_tehri <-  responses_tehri[, c(1, 69:71)] |>
  rename(
    x1st_preference = x1st_choice_68,
    x2nd_preference = x2nd_choice_69,
    x3rd_preference = x3rd_choice_70
	) |> 
	pivot_longer(cols = -respondent_id,
		names_to = "preference", 
		values_to = "sdg_label") |>
		mutate(response_id = str_c(respondent_id, "_", preference))

source_top_3_tehri

```


### SDG labelling

```{r}
# Read file and clean names
source_sdg <- read_csv(here("data-raw", "SDG.csv")) |> 
	cleanup_colnames() |>
	rename(sdg_id = sdg, sdg_label = name) |>
	mutate(sdg_id = str_replace(sdg_id, "SDG", "SDG "))

# Dimensions of data
dim(source_sdg)

print(source_sdg)

```

```{r}
# source sdg original
source_sdg 

# generate source_sdg from tehridataset with labels
source_sdg <- source_top_3_tehri |> 
	select(sdg_label) |> 
	distinct() |>
	mutate(sdg_id = case_when(
		str_detect(sdg_label, "biodiversity") ~ "SDG 15",
		str_detect(sdg_label, "Food") ~ "SDG 2",
		str_detect(sdg_label, "Livelihood") ~ "SDG 1",
		str_detect(sdg_label, "Education")  ~ "SDG 4",
		str_detect(sdg_label, "Gender") ~ "SDG 5",
		str_detect(sdg_label, "water")  ~ "SDG 6",
		str_detect(sdg_label, "energy") ~ "SDG 7",
		str_detect(sdg_label, "infrastructure") ~ "SDG 9",
		str_detect(sdg_label, "employment") ~ "SDG 8",
		str_detect(sdg_label, "climate") ~ "SDG 13",
		str_detect(sdg_label, "ineq") ~ "SDG 10",
		str_detect(sdg_label, "Global") ~ "SDG 17",
		str_detect(sdg_label, "wellbeing") ~ "SDG 3",
		str_detect(sdg_label, "inclusive") ~ "SDG 16",
		str_detect(sdg_label, "cities") ~ "SDG 11",
		str_detect(sdg_label, "resources") ~ "SDG 12",
		TRUE ~ "todo"
	)) |>
	arrange(sdg_id)


```

## Tidy up tehri  data sdg labels

```{r}

source_top_3_tehri <-
	source_top_3_tehri |>
		left_join(source_sdg, by = "sdg_label") |>
		select(-sdg_label)

```


## Check source-specifc semantic entity data

```{r}
#| message: true

source(here("R", "ge_unique_key.R"))

ge_unique_key(source_respondent_arunachal, "respondent_id")
ge_unique_key(source_respondent_tehri, "respondent_id")
ge_unique_key(source_top_3_arunachal, "response_id")
ge_unique_key(source_top_3_tehri, "response_id")
ge_unique_key(source_sdg, "sdg_id")

```


## Write source-specific semantic entity data

```{r}
source_path <- here("pipeline", "pipeline-data")

write_csv(source_sdg, here(source_path, "source_sdg.csv"))
write_csv(source_top_3_arunachal, here(source_path, "source_top_3_arunachal.csv"))
write_csv(source_top_3_tehri, here(source_path, "source_top_3_tehri.csv"))
write_csv(source_respondent_arunachal, here(source_path, "source_respondent_arunachal.csv"))
write_csv(source_respondent_tehri, here(source_path, "source_respondent_tehri.csv"))


```


