# Validation questions for Garima


```{r setup, include = FALSE}
knitr::opts_chunk$set(
    error = TRUE,
    message = FALSE
)
```

```{r pkg}

# pkg
library(tidyverse)
library(here)

# other things
pipeline_path <- here("pipeline", "pipeline-data")

```

> Garima: Do you expect this many respondents from Arunachal? 

```{r}

nrow(read_csv(here(pipeline_path, "staging_responses_arunachal.csv")))

```

> Garima: Do you expect this many respondents from Tehri?

```{r}

nrow(read_csv(here(pipeline_path, "staging_responses_tehri.csv")))

```


# Data validation notes

- focus was on dams
- two distinct geographic regions: Western Himalaya (Tehri) and Eastern Himalaya (Arunachal)
- Tehri is where the dam exists-commissioned in 2006, displaced 100K people
- lots of dam development in Arunachal 
- also a biodiversity hotspot, 80% forest cover

- what are the group-level community SDGs in Arunachal and Tehri? How might we interpret these results in light of the prioritisation of dams?

- region of focus was chosen because Arunachal has a lot of dam development, home to many diverse indigenous communities, and biodiversity as well

## Categories of respondents

- displaced (by dam)
- affected but not displaced (indirectly affected by dam)
- downstream (of the dam)
- benefitted by not affected (by the dam)

## Different experiments

- number of SDGs was restricted in one question
- number of SDGs unrestricted in another question
- Arunachal were not asked to choose five

## Respondents

- one group had a couple of hundred, the other group was much smaller 

## Notes

- two large geographic regions (Tehri vs Arunachal)
- two different sample sizes by region
- smaller communities in each region

## Data entities

- respondents + attributes
- SDG + attributes
- geograph regions + attributes
- preferences

# Poke the data with a stick

Have we identified all of the data entities required? 

## What artifacts did we get?

### Two barplots 

These were starting points. Garima didn't feel like she was answering all the questions she could with the datasets. 

These will be our initial migration.

### An R cleaning script
