# Validation questions for Garima

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    error = TRUE,
    message = FALSE
)
```

```{r pkg}
# pkg
library(tidyverse)
library(here)
library(readxl)

# other things
pipeline_path <- here("pipeline", "pipeline-data")
```

> Garima: Do you expect this many respondents from Arunachal? 

# Run pipeline

This chunk needs to be run before knitting so that the data exists. 

```{r eval=FALSE}
# Run extraction of entities from source
knitr::knit_child(here("pipeline", "fair-staging.Rmd"))

# Run semantic transformation of entities
knitr::knit_child(here("pipeline", "fair-semantic-transformation.Rmd"))

# Run analytical entities
knitr::knit_child(here("pipeline", "fair-analytical-observations.Rmd"))
```

# Source data validation

What tables are in this arrow? 

```{dot, fig.width=2, fig.height=2}

digraph G {
    rankdir=BT

    raw [label="data-raw/", shape=hexagon]
    raw -> source
}


```

## Load data

```{r}
# note that you can add as many columns as you like to these raw input datasets

raw_path <- "data-raw"

raw_responses_tehri <-
    read_csv(here(
        raw_path,
        "Dam_and_You_-_all_versions_-_labels_-_2023-06-21-12-49-55.csv"
    ))

raw_responses_arunachal <-
    read_excel(here(
        raw_path,
        "SDGPreferences_Arunachal.xlsx"
    ))

# you may wish to add more columns to SDGs, for example what top-level prioritise

raw_sdg <-
    read_csv(here(
        raw_path,
        "SDG.csv"
    ))
```

## Assumptions about raw arrow

The Lab understand the data to be one respondent's responses per row. 

> Q for Garima: Do you expect this many respondents from Arunachal?

```{r}
nrow(raw_responses_arunachal)
```

> Q for Garima: Do you expect this many respondents from Tehri?

```{r}
nrow(raw_responses_tehri)
```

Now to use the Good Enough Lab analogous test.

```{r}
# source the function
source(here("R", "ge_unique_key.R"))
```

Test each of the raw inputs on assumption on what columns  define a row.

```{r, message=TRUE}
# unique key test on arunachal responses
ge_unique_key(raw_responses_arunachal, "Respondents")

# unique key test on tehri responses, one row per respondent, no id
ge_unique_key(raw_responses_tehri |> mutate(respondent_id = 1:n()), "respondent_id")

# unique key test on sdg
ge_unique_key(raw_sdg, "SDG")
```

# Assumptions about the source extraction arrow

What are the tables in this arrow? 

```{dot, fig.width=2, fig.height=2}

digraph G {
    rankdir=BT

    source -> semantic
}


```

## Load data


```{r}
getwd()

here(pipeline_path, "staging_top_3_arunachal.csv")

```

```{r}

# read in responses from arunachal
source_top_3_arunachal <- read_csv(here(pipeline_path, "staging_top_3_arunachal.csv"))

# read in responses from tehri
source_top_3_tehri <- read_csv(here(pipeline_path, "staging_top_3_tehri.csv"))

# read in respondents from arunachal
source_respondent_arunachal <- read_csv(here(pipeline_path, "staging_respondent_arunachal.csv"))

# read in respondents from tehri
source_respondent_tehri <- read_csv(here(pipeline_path, "staging_respondent_tehri.csv"))

# read in sdg metadata
source_sdg <- read_csv(here(pipeline_path, "staging_sdg.csv"))

```


## Rankings by region

Important things to check. There is a response id that has the same dimensionality as the rank and respondent.

```{r, message=TRUE}
ge_unique_key(source_top_3_arunachal, "response_id")

```


```{r, message=TRUE}
ge_unique_key(source_top_3_tehri, "response_id")

```

We also need geographic.

```{r, message=TRUE}
table(source_respondent_tehri$region)

```


```{r, message=TRUE}
table(source_respondent_arunachal$region)

```



## SDG 

```{r, message=TRUE}
ge_unique_key(source_sdg, "sdg_id")


```

## Respondents by region

```{r, message=TRUE}
# check arunachal
ge_unique_key(source_respondent_arunachal, "respondent_id")

# check tehri
ge_unique_key(source_respondent_tehri, "respondent_id")


```



## Respondents by region

## SDG metadata


# Data validation notes

- focus was on dams
- two distinct geographic regions: Western Himalaya (Tehri) and Eastern Himalaya (Arunachal)
- Tehri is where the dam exists-commissioned in 2006, displaced 100K people
- lots of dam development in Arunachal 
- also a biodiversity hotspot, 80% forest cover

- what are the group-level community SDGs in Arunachal and Tehri? How might we interpret these results in light of the prioritisation of dams?

- region of focus was chosen because Arunachal has a lot of dam development, home to many diverse indigenous communities, and biodiversity as well

## Categories of respondents

- displaced (by dam)
- affected but not displaced (indirectly affected by dam)
- downstream (of the dam)
- benefitted by not affected (by the dam)

## Different experiments

- number of SDGs was restricted in one question
- number of SDGs unrestricted in another question
- Arunachal were not asked to choose five

## Respondents

- one group had a couple of hundred, the other group was much smaller 

## Notes

- two large geographic regions (Tehri vs Arunachal)
- two different sample sizes by region
- smaller communities in each region

## Data entities

- respondents + attributes
- SDG + attributes
- geograph regions + attributes
- preferences

# Poke the data with a stick

Have we identified all of the data entities required? 

## What artifacts did we get?

### Two barplots 

These were starting points. Garima didn't feel like she was answering all the questions she could with the datasets. 

These will be our initial migration.

### An R cleaning script
